---
title: "STOP Data Analysis Report"
author: "Julio Vega"
date: "15 August 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../data/common_source.R")
source("visualisations.R")
```
## If new data comes in run:

1. Correct the JSON formatting bug (comma instead of bracket) for P08 and P11 with `correct_ball_game_data_bug.R` (only if the study is still ongoing).
1. `sql_table_to_csv.R`. Takes a while because of game data.
1. `clean_data.R`. There is a second bug for P11 that produces bad JSON game data, if you find this, you need to look for the specific row (tail+print) and then add it to line 102 of `clean_data.R`
2. `generate_study_report.R`
3. Then `knit` this report

## Data dumping
All 4 tables `r tables_names` are dumped into CSV files using `sql_table_to_csv.R`

### Data dumping from a SQLite database
Put the SQLite database in data/raw/sqlite/pX and then run in Linux or WSL `python3 Migrating_data_from_SQLite_to_MySQL.py -se ../../data/raw/sqlite`

## Data cleaning 
Script `clean_data.R` does the following:

- For medication
    * It converts the DB timestamp into a date
    * It converts the medication timestamp into a date into `intake_time`
- For notifications
    - Translate period labels from Finish to English
    - Filter out buggy notifications
        - **TODO** Ask Yukki how notifications were logged on iOS, they are different compared to Android
        - **TODO** There's a possible bug on the notificion log in Android related to evening notifications. `filter_out_buggy_notifications` method is taking care of this but might no be 100% precise
- For diary survey
      - It converts the DB timestamp into a date
- For ball game
      - It converts the DB timestamp into a date
      - It splits the game sensors into 4 files: accelerometer, gyro, rotation, linear accelerometer, with the game date on each sensor row


## Data up to August 27th

Run script `generate_study_report.R` to update the report table.

Considerations:

- P01, P02, P03, P05, P07 are missing some data due to the certificate issue (have to update the app and sync manually). P01, 2, 4, 6, 7 have complete data now.

- P05 uninstalled the app before retriving data. Data is lost.

- We got P04's data from their SQLite database. Dumped to the server using `migrating_data_from_SQLite_to_MySQL.py`. 

- Ball game JSON data was malformed for P04, P07, P08, P11, fixed using `correct_ball_game_data_bug.R`. 1 game had invalid information for P04 `filter(X_id != 477)` and 3 for P11 `filter(_id != 1345 & _id != 1316 & _id != 5113)`.

- In ball game, the linear accelerometer and rotation records for P06 sometimes didn't have any values. Filtered those out.

- We have complete data from P06: 175 games, 178 medication logs, and 65 symptom survey (two per day). There was a bug with notifications, therefore there are no notification logs for this participant.


```{r echo=FALSE}
report = read.csv( "../../reports/study_report.csv",  stringsAsFactors = F)
knitr::kable(report, caption = "Study Report", align = "c")
```


## Medication intake
```{r echo=FALSE, fig.height=25, fig.width=15, warning=FALSE}

visualise_medication()
```

## Notification compliance

We have to notification events:

1. Shown
2. Open

We have five notification periods:

1. morning (8:00 - 11:59)
1. noon (12:00 - 14:59)
1. afternoon (15:00 - 18:59)
1. evening (19:00 - 21:59)
1. dailysymptoms (10:00 - 11:00)

Need to double check this data as iOS notifications and evening notifications on Android might be wrongly processed. **TODO** Dailys ymptoms rate is over 1.0 for P10. There was a bug in iOS notifications.

The mean time plot shows the SD as well. If there is no SD whiskers is because there was only 1 notification that was open after being shown

```{r echo=FALSE, fig.height=10, fig.width=15, warning=FALSE}
visualise_notifications()
```

## Diary scores

We have 5 posible scores 0-4

```{r echo=FALSE, fig.height=10, fig.width=15, warning=FALSE}
visualise_diary()
```

## Game scores

Game scores are averaged within bins of 30 or 60 minutes since their last medication

```{r echo=FALSE, fig.height=25, fig.width=15, warning=FALSE, message = FALSE}
visualise_meds_games()
```

## Game accelerometer data

Game accelerometer data within bins of 60 minutes since their last medication

```{r echo=FALSE, fig.height=105, fig.width=10, warning=FALSE, message = FALSE}
visualise_movement_sensor("ball_game_acc", "accelerometer")
```

## Game gyroscope data

Game gyroscope data within bins of 60 minutes since their last medication

```{r echo=FALSE, fig.height=105, fig.width=10, warning=FALSE, message = FALSE}
visualise_movement_sensor("ball_game_gyr", "gyroscope")
```

## Game rotation data

Game rotation data within bins of 60 minutes since their last medication

```{r echo=FALSE, fig.height=105, fig.width=10, warning=FALSE, message = FALSE}
visualise_movement_sensor("ball_game_rota", "rotation")
```

## Game linear accelerometer data

Game linear accelerometer data within bins of 60 minutes since their last medication

```{r echo=FALSE, fig.height=105, fig.width=10, warning=FALSE, message = FALSE}
visualise_movement_sensor("ball_game_lacc", "linear accelerometer")
```

## Game's mean/sd of sd of accelerometer magnitude data

Game mean/sd of the sd of accelerometer magnitude within bins of 30/60 minutes since their last medication

```{r echo=FALSE, fig.height=25, fig.width=15, warning=FALSE, message = FALSE}
visualise_sd_sensor_games("ball_game_acc", "accelerometer")
```

## Game's mean/sd of sd of gyroscope magnitude data

Game mean/sd of the sd of gyroscope magnitude within bins of 30/60 minutes since their last medication

```{r echo=FALSE, fig.height=25, fig.width=15, warning=FALSE, message = FALSE}
visualise_sd_sensor_games("ball_game_gyr", "gyroscope")
```

## Game's mean/sd of sd of rotation magnitude data

Game mean/sd of the sd of rotation magnitude within bins of 30/60 minutes since their last medication

```{r echo=FALSE, fig.height=25, fig.width=15, warning=FALSE, message = FALSE}
visualise_sd_sensor_games("ball_game_rota", "rotation")
```

## Game's mean/sd of sd of linear accelerometer magnitude data

Game mean/sd of the sd of linear accelerometer magnitude within bins of 30/60 minutes since their last medication. **TODO** why are there less linear accelerometer games than accelerometer games?

```{r echo=FALSE, fig.height=25, fig.width=15, warning=FALSE, message = FALSE}
visualise_sd_sensor_games("ball_game_lacc", "linear accelerometer")
```

